The error when inferring phylogenies with incipient species by a Birth-Death model

### 2018-04-17 article.tex
Use correct MCMC chain length
Use half of max size, 20K rows

From an alignment, we run a Bayesian analysis and create a posterior, 
using the phylogetic tool BEAST2 \cite{beast2} using the 
pirouette (\cite{pirouette}) package. As our site model, we assume a Jukes-Cantor 
nucleotide substitution model, as we used that in the simulation of the alignment.
For our clock model, we assume a strict clock with the same fixed rate as 
used in the simulation of the alignment. The tree prior assumed is the BD model, 
as this simplification is the goal of this research. 
Additionally, we assume a MRCA prior with a normal distribution
with a mean of the crown age, and a standard deviation of 0.001 time units. 0.001
time units equates to 1000 years, which is the same resolution as which the
alignment is created. The MCMC chain is run to generate 1100 states,
of which the first 10\% (also called the 'burn-in') is removed. Of the remaining
1000 MCMC states [NOTE: Why 1000? Why not 250?], 
the effective sample size (ESS) of the posterior must at least be 200
for a strong enough inference (\cite{beastbook}). An ESS can be increased by increasing
the number of samples or decreasing the autocorrelation between samples. 
Would the ESS be less than 200, we decrease autocorrelation by doubling 
the MCMC sampling interval of that simulation, until the ESS exceeds 200.

@@

Each data set will be stored as a comma-seperated file. We placed 
an upper limit for this data set's size at the maximum size of a table (called 
a data frame) of the R programming language, in which such a table may 
have maximally $2^{32}-1$ cells and occupy less then 2 gigabytes in memory.
Each row will contain the parameter set, nLTT statistics and some 
diagnostics [NOTE: should I keep the diagnostics?] (see \ref{table:specs} for the 
complete list). From the constraints of the R programming language, this allows for 40K rows.

>>>>

From an alignment, we run a Bayesian analysis and create a posterior, 
using the phylogetic tool BEAST2 \cite{beast2} using the 
pirouette (\cite{pirouette}) package. As our site model, we assume a Jukes-Cantor 
nucleotide substitution model, as we used that in the simulation of the alignment.
For our clock model, we assume a strict clock with the same fixed rate as 
used in the simulation of the alignment. The tree prior assumed is the BD model, 
as this simplification is the goal of this research. 
Additionally, we assume a MRCA prior with a normal distribution
with a mean of the crown age, and a standard deviation of 0.001 time units. 0.001
time units equates to 1000 years, which is the same resolution as which the
alignment is created. The MCMC chain is run to generate 1111 states,
of which the first 10\% (also called the 'burn-in') is removed. Of the remaining
1000 MCMC states [NOTE: Why 1000? Why not 250?], 
the effective sample size (ESS) of the posterior must at least be 200
for a strong enough inference (\cite{beastbook}). An ESS can be increased by increasing
the number of samples or decreasing the autocorrelation between samples. 
Would the ESS be less than 200, we decrease autocorrelation by doubling 
the MCMC sampling interval of that simulation, until the ESS exceeds 200.

@@

Each data set will be stored as a comma-seperated file. We placed 
an upper limit for this data set's size at the maximum size of a table (called 
a data frame) of the R programming language, in which such a table may 
have maximally $2^{32}-1$ cells and occupy less then 2 gigabytes in memory.
To provide for copying such a table (thus, allowing it to be present in
memory twice), the size of the table has an upper limit of half its maximal size.
Each row will contain the parameter set and the generated nLTT 
statistics (see \ref{table:specs} for the exact data specification).
From these constraints, this allows for 20K rows.
